Manuscript_Github_Pchabaudi_pir

### 2022-07-25 chapter4_results_chabaudi24h/Thesis_Github_Pchabaudi_pirAnalysis.Rmd
Save phaseogram plots in each order for all and pir genes

draw_heatmap_zscore(zscore_list = chab_z.list,
                    gene_ordering_vector = phaseogram_time_order$SBP$zscore_order$Geneid,
                    use_times = TRUE,
                    use_order_vector = FALSE,
                    show_row_names = FALSE,
                    tpm_mat = TRUE)

@@

if(global_save_var){
 pdf(file = 'Manuscript_SuppFig6_phaseogram_cirgenes.pdf',
      height = 5,
      width = 5)
  draw_heatmap_zscore(zscore_list = chab_z.list,
                      gene_ordering_vector = phaseogram_time_order$rMT$zscore_order$Geneid,
                      filter_genes_vector = cir_id,
                      annotation_clade = 'SorL',
                      annotation_col = SorL_col,
                      threshold_tpm = 1,
                      use_times = TRUE,
                      use_order_vector = FALSE,
                      show_row_names = FALSE,
                      tpm_mat = FALSE)
  dev.off()
}

draw_heatmap_zscore(zscore_list = chab_z.list,
                    gene_ordering_vector = phaseogram_time_order$SBP$zscore_order$Geneid,
                    filter_genes_vector = cir_id,
                    annotation_clade = 'SorL',
                    annotation_col = SorL_col,
                    threshold_tpm = 1,
                    use_times = TRUE,
                    use_order_vector = FALSE,
                    show_row_names = FALSE,
                    tpm_mat = TRUE)

>>>>

if(global_save_var){
  pdf(file = 'plots/phaseogram_allgenes_SBPorder.pdf',
      height = 5,
      width = 5)
draw_heatmap_zscore(zscore_list = chab_z.list,
                    gene_ordering_vector = phaseogram_time_order$SBP$zscore_order$Geneid,
                    use_times = TRUE,
                    use_order_vector = FALSE,
                    show_row_names = FALSE,
                    tpm_mat = TRUE)
  dev.off()
}

@@

if(global_save_var){
 pdf(file = 'plots/phaseogram_pirgenes_rMTorder.pdf',
      height = 5,
      width = 5)
  draw_heatmap_zscore(zscore_list = chab_z.list,
                      gene_ordering_vector = phaseogram_time_order$rMT$zscore_order$Geneid,
                      filter_genes_vector = cir_id,
                      annotation_clade = 'SorL',
                      annotation_col = SorL_col,
                      threshold_tpm = 1,
                      use_times = TRUE,
                      use_order_vector = FALSE,
                      show_row_names = FALSE,
                      tpm_mat = FALSE)
  dev.off()
}

if(global_save_var){
 pdf(file = 'plots/phaseogram_pirgenes_SBPorder.pdf',
      height = 5,
      width = 5)
draw_heatmap_zscore(zscore_list = chab_z.list,
                    gene_ordering_vector = phaseogram_time_order$SBP$zscore_order$Geneid,
                    filter_genes_vector = cir_id,
                    annotation_clade = 'SorL',
                    annotation_col = SorL_col,
                    threshold_tpm = 1,
                    use_times = TRUE,
                    use_order_vector = FALSE,
                    show_row_names = FALSE,
                    tpm_mat = TRUE)
  dev.off()
}
